Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-26 ms.tex
random3

Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.  If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
\end{align} The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq
\epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon$
with which the initial blast wave energy is converted into bulk or turbulent
motion instead of being lost to radiation.  \cite{Thornton+98}
estimate a radiative efficiency $\epsilon_{\rm Ia} \sim 0.1$,
depending weakly on surrounding density, but \citet{Sharma+14} argues
that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.  We hereafter adopt $\epsilon_{\rm Ia} = 0.4$.

>>>>

Type Ia supernovae (SNe Ia) represent a potentially important source of heating, which unlike core collapse SNe is present even in an evolved stellar population.  If each Ia supernova injects thermal energy $E_{\rm Ia}$ into the interstellar medium, and the SNe rate (per stellar mass) is given by $R_{\rm   Ia}$, then the resulting volumetric heating rate $E_{\rm Ia}R_{\rm  Ia}$ produces an effective wind heating parameter (equation~[\ref{eq:vw_eff}]) \begin{align} v_{w}^{\rm Ia} =\sqrt{\frac{2 t_h R_{\rm Ia}
E_{\rm Ia}}{\eta}} \label{eq:vw_sne}.
\end{align} The thermal energy injected by a Ia SN $E_{\rm Ia} \simeq
\epsilon_{\rm Ia} 10^{51}$ ergs depends on the efficiency $\epsilon_{\rm Ia}$
with which the initial blast wave energy is converted into bulk or turbulent
motion instead of being lost to radiation.  \cite{Thornton+98}
estimate a radiative efficiency $\epsilon_{\rm Ia} \sim 0.1$,
depending weakly on surrounding density, but \citet{Sharma+14} argues
that $\epsilon_{\rm Ia}$ can be considerably higher, $\sim 0.4$, if
the SNe occur in a hot dilute medium, as may characterize the circumnuclear medium.  We hereafter adopt $\epsilon_{\rm Ia} = 0.4$.
